The complex network of trophic interactions in a subAntarctic Marine Protected

### 2023-01-26 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Submission formatting

---
title: The complex network of trophic interactions in a subAntarctic Marine Protected
  Area
author: "Tomás I. Marina, Irene R. Schloss and Luciana Riccialdelli"
output:
  pdf_document: default
  word_document: default
bibliography: AMPBancoBurdwood.bib
csl: "marine-ecology-progress-series.csl"
nocite: '@*'
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
---

@@

## Abstract

## Introduction

Brief description and ecological importance of MPAN-BB

@@

Benefits of studying complex ecosystems using network approach

Objective
In the present work we present the first, detailed analysis of the food web for the MPA Namuncurá - Banco Burdwood ecosystem. For this we applied a network approach to a highly-resolved food web. The objective was twofold: characterise the food web in terms of complexity and structure, and describe the species' role in such network framework.

## Methodology

### Study area

The MPA Namuncurá-Banco Burdwood is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1). It comprises nearly 34.000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west. The BB is surrounded by steep flanks of more than 3000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019]. Intense upwelling and mixing occur over it, entraining deep nutrient rich waters into the photic layer [@Piola2009; @Matano2019], and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019]. Physical features in the MPAN-BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC overall [@Guerrero1999; @Acha2004; @Piola2009].

```{r figure1, echo=FALSE, out.width = '100%', fig.cap="Map of the Marine Protected Area Namuncurá-Banco Burdwood. Taken from https://www.argentina.gob.ar/parquesnacionales/areasmarinas/namuncura-burdwood."}
# Map of MPAN-BB provided by Lu R. (?)
knitr::include_graphics("MPABurdwood_map.jpeg")

@@

### Network construction

@@

### Network analysis

We analysed the MPA Namuncurá-Banco Burdwood network of trophic interactions, hereafter food web, at two levels: 1) global, considering species and interactions of the whole network; and 2) species, considering interactions and species related to a particular species. The global-level analysis aims to characterize the network of trophic interactions in terms of complexity and structure. For this we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) Connectance L/S^2; (5) omnivory Omn; and (6) shortest path length SPL. Also, we estimated the (7) degree distributions for the food web, for prey and predators, and for each functional group (e.g. Amphipoda, Ascidiacea, Bivalvia, Fish, Marine mammals, Seabirds, etc.) (Table 1). The prey and predator distributions indicate the frequency of prey among predators, and viceversa; the functional group's degree shows the distribution of interactions within groups.
The species-level analysis aims to describe the species' role in the food web. For this we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic similarity TS; (4) topological role TR; and (5) trophic level TL (Table 1). We also studied the relationship between species trophic level and the other species properties by performing linear regression analyses. Thus, we considered the IS as the dependent variable and the given unweighted property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model. Models were fitted using the least squares approach. We also explored the mean IS distribution with the species habitat.
These properties provide a general appropriate description of species' role in empirical complex food webs [@Cirtwill2018].

@@

table1 <- add_row(table1, Name="Degree distribution", Definition="Probability of trophic species P(k) that have k or more interactions (both predator and prey links).", Implications="It suggests on the vulnerability of complex food webs against random failures and intentional attacks (i.e. species extinctions).", Reference="Albert & Barabási 2002")

@@

names(table1) <- pandoc.strong.return(names(table1))
pandoc.table(table1, digits = 4, colnames("Property","Definition","Implication","Reference"), style="multiline", split.tables = Inf, justify = c('left','left','left','right'), emphasize.strong.cols = 1, emphasize.rownames = 1,
             caption = "List of network properties analysed, definitions, and relevant ecological implications related to food web complexity and structure.")

@@

@@

## Results

### Network-level properties

```{r figure2, echo=FALSE, fig.align='center', fig.width = 20, fig.height=20, fig.cap="Graph of the food web of MPA Namuncurá-Banco Burdwood. Circles represent species and arrows trophic interactions. Colour gradient indicate the trophic level. Circle diameter is relative to the number of interactions."}
# Food web graph

@@

par(cex.axis=1.5, cex.lab=1.5)
figure_2 <- plot_troph_level(g, vertexLabel = F, modules = F, ylab = "Trophic level")

@@

knitr::kable(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength), col.names = c("Species","Interactions","Density","Connectance","Omnivory","Path length"),
                      caption = "Global-level properties of the MPA Namuncurá-Banco Burdwood food web. See table 1 for definitions and ecological relevance.") %>% row_spec(0,bold=TRUE)

@@

The degree distribution of the food web showed an asymmetric frequency in the number of interactions, where most of the species had a relatively low number of interactions and few species concentrated the majority of them (Figure 3A). If we consider the distribution of prey among predators, most of the consumers fed on a low number of prey whereas few of them had multiple preys (Figure 3B). These were the top-five predators in terms of prey: *Patagonotothen guntheri* (Notothenioid fish, 52 prey), *Patagonotothen ramsayi* (Notothenioid fish, 50 prey), *Dissostichus eleginoides* (Notothenioid fish, 30 prey), *Bathyraja brachyurops* (Chondrichthyan, 30 prey), and *Bathyraja griseocauda* (Chondrichthyan, 28 prey). Following the same distribution pattern, few prey presented multiple predators (Figure 3C). These were the top-five prey in number of predators: Detritus (Non-living, predators), the three categories of Diatoms considered (benthic, centric and pennate, 72 predators on average), and species of genus *Euphausia* (Zooplankton, 46 predators). Finally, taking into account the interactions within each functional group, the situation is the same as in the whole food web (Figure 3D). Overall, there is an evident asymmetry in the distribution of interactions among species in the MPA Namuncurá-Banco Burdwood food web.

@@

```{r figure3, echo=FALSE, fig.height = 25, fig.width = 20, fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group. Groups are vertically ordered by increasing trophic level."}
# Degree distributions: network, predator, prey & group
# above row (network, prey, predator), below row (group)

@@

# Network Degree
degree <- as.data.frame(degree(g, mode = "total"))
plot_totdeg <- ggplot(degree, aes(degree[,1])) +
    geom_histogram(bins = 100, alpha = 0.3, color = "black") +
    labs(x = "Number of interactions (Degree)", y = "Frequency") +
    theme_bw() +
    theme(legend.position = "none",
          axis.text.x = element_text(size = 26),
          axis.text.y = element_text(size = 26),
          axis.title.x = element_text(face = "bold", size = 26),
          axis.title.y = element_text(face = "bold", size = 26))

# Predator Degree
# Generality (generalistas vs especialistas)
plot_preddeg <- spp_total %>% 
    filter(NumPrey != 0) %>% 
    ggplot(., aes(x = NumPrey)) +
    geom_histogram(stat = "count") +
    labs(x = "Predators", y = "Number of prey") +
    theme_bw() +
    theme(legend.position = "none",
          axis.text.x = element_text(size = 26),
          axis.text.y = element_text(size = 26),
          axis.title.x = element_text(face = "bold", size = 26),
          axis.title.y = element_text(face = "bold", size = 26)) #+
# annotate("text", x = Inf, y = Inf, label = paste("Prey per predator = ", round(prop_topol$Generality, 2), sep = ""),
#          size = 5, vjust=1, hjust=1))

# Prey Degree
# Vulnerability (energy flows)
plot_preydeg <- spp_total %>% 
    filter(NumPred != 0) %>% 
    ggplot(., aes(x = NumPred)) +
    geom_histogram(stat = "count") +
    labs(x = "Prey", y = "Number of predators") +
    theme_bw() +
    theme(legend.position = "none",
          axis.text.x = element_text(size = 26),
          axis.text.y = element_text(size = 26),
          axis.title.x = element_text(face = "bold", size = 26),
          axis.title.y = element_text(face = "bold", size = 26)) #+
# annotate("text", x = Inf, y = Inf, label = paste("Predators per prey = ", round(prop_topol$Vulnerability, 2), sep = ""),
#          size = 5, vjust=1, hjust=1))

@@

plot_grpdeg <- spp_total %>% 
    add_count(FunctionalGroup) %>% 
    filter(n > 2) %>% 
    group_by(FunctionalGroup) %>% 
    mutate(TL_fg = mean(TL)) %>% 
    ggplot(., aes(x = TotalDegree, y = reorder(FunctionalGroup, TL_fg), fill = FunctionalGroup)) + 
    geom_joy(scale = 3.75) +
    scale_fill_manual(values = FGColors) +
    labs(x = "Number of interactions", y = "Functional group", tag="D") +
    theme_joy(grid = FALSE) +
    theme(legend.position = "none",
          axis.text.x = element_text(size = 26),
          axis.text.y = element_text(size = 20),
          axis.title.x = element_text(face = "bold", size = 26),
          axis.title.y = element_text(face = "bold", size = 26),
          plot.tag = element_text(face = "bold", size = 32),
          plot.tag.position = c(0.05, 1))

@@

# Move to a new page
grid.newpage()
# Nested ggarrange
figure_3 <- ggarrange(a,                                                                                         # First row
          ggarrange(b, c, ncol = 2, labels = c("B", "C"), font.label=list(color="black",size=30)),   # Second row
          ggarrange(d, ncol = 1),                                                                    # Third row
          nrow = 3, labels = "A",
          font.label=list(color="black",size=30))
figure_3

@@

### Species-level properties

@@

We found different relationships between the species trophic level (TL) and the rest of the analysed species-level properties (Figure 4A-D). In this regard, the most evident significant relationship was with trophic similarity, i.e. the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C). Here we highlight the following high-trophic level species of fishes (*Bathyraja macloviana*, *Squalus acanthias*), echinoderms (*Diplopteraster clarki*, *Pteraster sp*), seabirds (*Phalacrocorax_atriceps*, *Eudyptes chrysocome*), and marine mammals (*Lagenorhynchus_cruciger*, *Mesoplodon_bowdoini*) (Table S3).
There was also a negative significant relationship with closeness, however less strong: low-TL species were relatively closer to any other species in the food web than high-TL ones (Figure 4B). Species of genera *Calanus* and *Euphausia*, and Brachiopoda trophic species, all of them with TL < 3, registered the highest values (Table S3).
It's noteworthy that the highest values of betweenness were shown by species of mid-TLs (3-4), meaning that those species participated in the highest number of shortest paths between species (Figure 4A). These were the species with the highest values: *Patagonotothen ramsayi*, *Dissostichus eleginoides*, *Salilota australis* (fish), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Table S3).
Taking into account the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework). Here it's important to highlight species of the latter two topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.

@@

```{r figure4, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Species-level properties (A) betweenness, (B) closeness, (C) trophic similarity, and (D) topological role by trophic level. Each point represents a species. Linear regressions for betweenness ($y = 72.48x - 111.98, R^2 = 0.04, p-value < 3.38e-05$), closeness ($y = 5.78e-06x - 9.37e-04, R^2 = -0.0005, p-value = 0.37$) and trophic similarity ($y = -0.01x - 0.11, R^2 = 0.07, p-value = 6.76e-08$). Note that for A, B and C panels only species with TLs equal or greater than 2 were considered."}
# Betweenness, Closeness, Trophic similarity & Topological role by Trophic level

@@

# Betweenness
plot_sp_bt <- spp_total %>% 
  filter(TL >= 2) %>% 
  ggplot(., aes(x = TL, y = Between)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Trophic level", y = "Betweenness") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 26),
        axis.text.y = element_text(size = 26),
        axis.title = element_text(size = 26, face = "bold"))

# Closeness
plot_sp_cl <- spp_total %>% 
  filter(TL >= 2) %>%
  ggplot(., aes(x = TL, y = Close)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Trophic level", y = "Closeness") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 26),
        axis.text.y = element_text(size = 26),
        axis.title = element_text(size = 26, face = "bold"))

# Trophic similarity
plot_sp_ts <- spp_total %>% 
  filter(TL >= 2) %>%
  ggplot(., aes(x = TL, y = meanTrophicSimil)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Trophic level", y = "Trophic similarity") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 26),
        axis.text.y = element_text(size = 26),
        axis.title = element_text(size = 26, face = "bold"))

@@

cols <- c("netcon"="#492050", "modspe"="#023903", "modhub"="#A5CEA5", "modcon"="#DAB8E2")
plot_sp_tr <- spp_total %>% 
  mutate(TopRole = case_when(TopRole == "hubcon" ~ "netcon", TRUE ~ TopRole)) %>% 
  ggplot(., aes(x = TopRole, y = TL)) +
  geom_boxplot(aes(color = factor(TopRole), fill = factor(TopRole)), alpha=0.9) +
  geom_jitter(aes(color = factor(TopRole), fill = factor(TopRole))) +
  scale_fill_manual(values=cols) +
  labs(x = "Topological role", y = "Trophic level") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 26),
        axis.text.y = element_text(size = 26),
        axis.title = element_text(size = 26, face = "bold"),
        legend.position = "none")

# Move to a new page
grid.newpage()
# Arrange figure
figure_ab <- ggarrange(plot_sp_bt + rremove("xlab"), plot_sp_cl + rremove("xlab"),
                      labels = c("A","B"), ncol=2,
                      font.label = list(size = 30, color = "black"))
figure_ab <- annotate_figure(figure_ab, bottom = textGrob("Trophic level", gp = gpar(fontface="bold", col="black", fontsize=26)))
figure_4 <- ggarrange(figure_ab,                                                                                         # First row
          ggarrange(plot_sp_ts, plot_sp_tr, ncol = 2, labels = c("C", "D"), font.label=list(color="black",size=30)),                                            
          nrow = 2)
figure_4

@@

## Discussion

### The MPA Namuncurá - Banco Burdwood food web

* The MPA Namuncurá - Banco Burdwood food web is one of the most highly-resolved network of trophic interactions described for subpolar and polar regions.
Compare with other subpolar and polar food webs.

* The food web shows an asymmetry in the distribution of interactions at several levels: food web, functional group, prey and predators. In all of them interactions are concentrated in a few species.
On one hand, this asymmetry indicates that most consumers have a narrow diet, few present flexible diets (Patagonotothen guntheri, P. ramsayi, Dissostichus eleginoides, Bathyraja brachyurops, B. griseocauda).
On the other hand few prey are consumed by many predators, meaning that there are dominant food sources from which most consumers depend on: detritus, diatoms (benthic, centric, pennate), and species of *Euphausia*.

### Species' role

@@

* Betweenness. Species at mid-trophic levels (3-4) lie in more shortest paths between species than any other species: ‘bridge’ role. Implications for spread of perturbations like mercury, microplastics.

* Closeness. Low-trophic level species are relatively closer to other species in the food web.

* Trophic similarity. Species are more similar at low and mid-trophic levels (2-4). There is a functional redundancy at these levels of the food web. On the other hand, less trophic similarity at high levels indicate uniqueness in terms of trophic role. This highlights the importance of top predators.

* Topological role. network connector and module connector species are responsible for linking modules and maintaining the connectivity of the food web. TL range for these species: 1 - 3.86. Low and mid-trophic level species are responsible for maintaining the connectivity of the food web. The functional groups represented are: Amphipoda, Bivalvia, Bryozoa, Cnidaria, Cumacea, Decapoda, Detritus, Diatoms, Echinodermata, Fish (bentho-pelagic, demersal, chondrichthyes), Foraminifera, Polychaeta, Porifera, Zooplankton.

>>>>

---
title: The complex network of trophic interactions in a subAntarctic Marine Protected
  Area
author:
  - name: Tomás I. Marina^a^
    email: tomasimarina@gmail.com
  - name: Irene R. Schloss^a^^,^^b^
  - name: Luciana Riccialdelli^a^
address:
  - code: 1
    address: Centro Austral de Investigaciones Cientificas (CADIC-CONICET), Argentina
  - code: 2
    address: Instituto Antartico Argentino (IAA), Argentina
abstract: |
  The abstract goes here.

keywords: 
  - Food web
  - Complexity
  - Structure
  - Marine Protected Area
  - Southwest Atlantic
journal: "MEPS, Oikos, Polar Biology (?)"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: AMPBancoBurdwood.bib
nocite: '@*'
linenumbers: true
numbersections: true
# Use a CSL with `citation_package = "default"`
csl: "apa-old-doi-prefix.csl"
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: "default"
---

@@

# Introduction

Introduction to MPAs and MPA N-BB

Ecological importance of MPA N-BB to the region

@@

Why using a network approach

In the present work we present the first, detailed analysis of the food web for the MPA Namuncurá - Banco Burdwood ecosystem. For this we applied a network approach to a highly-resolved food web. The objective was twofold: characterise the food web in terms of complexity and structure, and describe the species' role in such network framework.

# Methodology

## Study area

The MPA Namuncurá - Banco Burdwood is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1). It comprises nearly 34.000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west. The BB is surrounded by steep flanks of more than 3000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019]. Intense upwelling and mixing occur over it, entraining deep nutrient rich waters into the photic layer [@Piola2009; @Matano2019], and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019]. Physical features in the MPAN-BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC overall [@Guerrero1999; @Acha2004; @Piola2009].

```{r figure1, echo=FALSE, fig.width = 5, fig.height = 10, out.width = '100%', fig.cap="Map of the Marine Protected Area Namuncurá - Banco Burdwood. Taken from https://www.argentina.gob.ar/parquesnacionales/areasmarinas/namuncura-burdwood."}
# Map of MPAN-BB provided by Lu R. (?)
knitr::include_graphics("MPABurdwood_map.jpeg")

@@

## Network construction

@@

## Network analysis

We analysed the MPA Namuncurá - Banco Burdwood network of trophic interactions, hereafter food web, at two levels: 1) network, considering species and interactions of the whole network; and 2) species, considering interactions and species related to a particular species. The network-level analysis aims to characterize the network of trophic interactions in terms of complexity and structure. For this we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) Connectance L/S^2; (5) omnivory Omn; and (6) shortest path length SPL. Also, we estimated the (7) degree distributions for the food web, for prey and predators, and for each functional group (e.g. Amphipoda, Ascidiacea, Bivalvia, Fish, Marine mammals, Sea birds, etc.) (Table 1). The prey and predator distributions indicate the frequency of prey among predators, and viceversa; the functional group's degree shows the distribution of interactions within groups.
The species-level analysis aims to describe the species' role in the food web. For this we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic similarity TS; (4) topological role TR; and (5) trophic level TL (Table 1). We also studied the relationship between species trophic level and the other species properties by performing linear regression analyses. Thus, we considered the IS as the dependent variable and the given unweighted property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model. Models were fitted using the least squares approach. We also explored the mean IS distribution with the species habitat.
These properties provide a general appropriate description of species' role in empirical complex food webs [@Cirtwill2018].

@@

table1 <- add_row(table1, Name="Degree distribution", Definition="Frequency of trophic species that have k or more interactions.", Implications="It suggests on the vulnerability of complex food webs against random failures and intentional attacks (i.e. species extinctions).", Reference="Albert & Barabási 2002")

@@

names(table1) <- pandoc.strong.return(names(table1))
pandoc.table(table1, digits = 4, colnames("Property","Definition","Implication","Reference"), style="multiline", split.tables = Inf, justify = c('left','left','left','right'), emphasize.strong.cols = 1, emphasize.rownames = 1,
             caption = "List of network and species-level properties analysed, definitions, and relevant ecological implications related to food web complexity and structure.")

@@

# Results

## Network-level properties

@@

```{r figure2, echo=FALSE, fig.width = 5.5, fig.height = 10, fig.align='center', fig.cap="Graph of the food web for the MPA Namuncurá - Banco Burdwood. Circles represent species and arrows trophic interactions. Circle diameter is relative to the number of interactions. Colour gradient indicate the trophic level."}
# Food web graph

@@

par(cex.axis=0.8, cex.lab=0.8)
figure_2 <- plot_troph_level(g, vertexLabel = F, modules = F, ylab = "Trophic level")

@@

knitr::kable(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength), col.names = c("Species","Interactions","Density","Connectance","Omnivory","Path length"),
                      caption = "Network-level properties of the MPA Namuncurá - Banco Burdwood food web. See table 1 for definitions and ecological relevance.") %>% row_spec(0,bold=TRUE)

@@

The degree distribution of the food web showed an asymmetric frequency in the number of interactions, where most of the species had a relatively low number of interactions and few species concentrated the majority of them (Figure 3A). The distribution of prey among predators showed that most of the consumers fed on a low number of prey whereas few of them had multiple preys (Figure 3B). These were the top-five predators in number of prey: *Patagonotothen guntheri* (Notothenioid fish, 52 prey), *Patagonotothen ramsayi* (Notothenioid fish, 50 prey), *Dissostichus eleginoides* (Notothenioid fish, 30 prey), *Bathyraja brachyurops* (Chondrichthyan, 30 prey), and *Bathyraja griseocauda* (Chondrichthyan, 28 prey). Following the same distribution pattern, few prey presented multiple predators (Figure 3C). These were the top-five prey in number of predators: Detritus (Non-living, 153 predators), the three categories of Diatoms considered (benthic, centric and pennate, 72 predators on average), and species of the genus *Euphausia* (Zooplankton, 46 predators). Finally, taking into account the interactions within each functional group, again the majority of the interactions were concentrated in few species (Figure 3D). The most evident species were: *Themisto gaudichaudii* (Amphipoda), *Zygochlamys patagonica* (Bivalvia), *Aspidostoma giganteum* (Bryozoa), *Munida gregaria* (Decapoda), *Patagonotothen ramsayi* and *Patagonotothen guntheri* (bentho-pelagic fish), *Psychrolutes marmoratus* (demersal fish), and species of *Euphausia* (Zooplankton).
Overall, there is an evident asymmetry in the distribution of interactions among species at different levels in the MPA Namuncurá - Banco Burdwood food web.

@@

```{r figure3, echo=FALSE, fig.width = 6.5, fig.height = 9, fig.align='center', fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group. Groups are vertically ordered by increasing trophic level; groups with less than 3 species were not plotted (e.g. pelagic fish)."}
# Degree distributions: network, predator, prey & group
# above row (network, prey, predator), below row (group)

@@

# Network Degree
degree <- as.data.frame(degree(g, mode = "total"))
plot_totdeg <- ggplot(degree, aes(degree[,1])) +
    geom_histogram(bins = 100, alpha = 0.3, color = "black") +
    labs(x = "Degree (total interactions)", y = "Frequency") +
    theme_bw() +
    theme(legend.position = "none",
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(face = "bold", size = 10),
          axis.title.y = element_text(face = "bold", size = 10))

# Predator Degree
# Generality (generalistas vs especialistas)
plot_preddeg <- spp_total %>% 
    filter(NumPrey != 0) %>% 
    ggplot(., aes(x = NumPrey)) +
    geom_histogram(stat = "count") +
    labs(x = "Predators", y = "Number of prey") +
    theme_bw() +
    theme(legend.position = "none",
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(face = "bold", size = 10),
          axis.title.y = element_text(face = "bold", size = 10)) #+
# annotate("text", x = Inf, y = Inf, label = paste("Prey per predator = ", round(prop_topol$Generality, 2), sep = ""),
#          size = 5, vjust=1, hjust=1))

# Prey Degree
# Vulnerability (energy flows)
plot_preydeg <- spp_total %>% 
    filter(NumPred != 0) %>% 
    ggplot(., aes(x = NumPred)) +
    geom_histogram(stat = "count") +
    labs(x = "Prey", y = "Number of predators") +
    theme_bw() +
    theme(legend.position = "none",
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(face = "bold", size = 10),
          axis.title.y = element_text(face = "bold", size = 10)) #+
# annotate("text", x = Inf, y = Inf, label = paste("Predators per prey = ", round(prop_topol$Vulnerability, 2), sep = ""),
#          size = 5, vjust=1, hjust=1))

@@

plot_grpdeg <- spp_total %>% 
    add_count(FunctionalGroup) %>% 
    filter(n > 2) %>% 
    group_by(FunctionalGroup) %>% 
    mutate(TL_fg = mean(TL)) %>% 
    ggplot(., aes(x = TotalDegree, y = reorder(FunctionalGroup, TL_fg), fill = FunctionalGroup)) + 
    geom_joy(scale = 3.75) +
    scale_fill_manual(values = FGColors) +
    labs(x = "Number of interactions", y = "Functional group", tag="D") +
    theme_joy(grid = FALSE) +
    theme(legend.position = "none",
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 6),
          axis.title.x = element_text(face = "bold", size = 10),
          axis.title.y = element_text(face = "bold", size = 10),
          plot.tag = element_text(face = "bold", size = 10),
          plot.tag.position = c(0.05, 1))

@@

# Move to a new page
grid.newpage()
# Nested ggarrange
figure_3 <- ggarrange(a,                                                                                         # First row
          ggarrange(b, c, ncol = 2, labels = c("B", "C"), font.label=list(color="black",size=10)),   # Second row
          ggarrange(d, ncol = 1),                                                                    # Third row
          nrow = 3, labels = "A",
          font.label=list(color="black",size=10))
figure_3

@@

## Species-level properties

@@

We found different relationships between the species trophic level (TL) and the rest of the analysed species-level properties (Figure 4A-D). In this regard, the most evident significant relationship was with trophic similarity, i.e. the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C). Here it's noteworthy to highlight high-trophic level species with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax_atriceps* and *Eudyptes chrysocome* (sea birds), and *Lagenorhynchus cruciger* and *Mesoplodon bowdoini* (marine mammals) (Table S3).

We also found a negative significant relationship with closeness, however less evident, meaning that low-TL species are relatively closer to any other species in the food web (Figure 4B). Species of genera *Calanus* and *Euphausia*, and species of Brachiopoda, all of them with TL < 3, registered the highest values of closeness (Table S3).

It's noteworthy that the highest values of betweenness were shown by species of mid-TLs (3-4), meaning that those species participated in the highest number of shortest paths between species (Figure 4A). These were the species with the highest values: *Patagonotothen ramsayi*, *Dissostichus eleginoides*, *Salilota australis* (fishes), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Notothenioid fish) (Table S3).

Taking into account the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework). Here it's important to highlight species of the two latter topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.

@@

```{r figure4, echo=FALSE, fig.width = 6.5, fig.height = 6.5, fig.align='center', fig.cap="Species-level properties by trophic level: (A) betweenness, (B) closeness, (C) trophic similarity, and (D) topological role. Each point represents a species. Linear regressions for betweenness ($y = 72.48x - 111.98, R^2 = 0.04, p-value < 3.38e-05$), closeness ($y = 5.78e-06x - 9.37e-04, R^2 = -0.0005, p-value = 0.37$) and trophic similarity ($y = -0.01x - 0.11, R^2 = 0.07, p-value = 6.76e-08$). Note that for A, B and C panels only species with TLs equal or greater than 2 were considered."}
# Betweenness, Closeness, Trophic similarity & Topological role by Trophic level

@@

# Betweenness
plot_sp_bt <- spp_total %>% 
  filter(TL >= 2) %>% 
  ggplot(., aes(x = TL, y = Between)) +
  geom_point(size=0.3) +
  geom_smooth(method = "lm") +
  labs(x = "Trophic level", y = "Betweenness") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title = element_text(size = 10, face = "bold"))

# Closeness
plot_sp_cl <- spp_total %>% 
  filter(TL >= 2) %>%
  ggplot(., aes(x = TL, y = Close)) +
  geom_point(size=0.3) +
  geom_smooth(method = "lm") +
  labs(x = "Trophic level", y = "Closeness") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title = element_text(size = 10, face = "bold"))

# Trophic similarity
plot_sp_ts <- spp_total %>% 
  filter(TL >= 2) %>%
  ggplot(., aes(x = TL, y = meanTrophicSimil)) +
  geom_point(size=0.3) +
  geom_smooth(method = "lm") +
  labs(x = "Trophic level", y = "Trophic similarity") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title = element_text(size = 10, face = "bold"))

@@

cols <- c("netcon"="#492050", "modspe"="#023903", "modhub"="#A5CEA5", "modcon"="#DAB8E2")
plot_sp_tr <- spp_total %>% 
  mutate(TopRole = case_when(TopRole == "hubcon" ~ "netcon", TRUE ~ TopRole)) %>% 
  ggplot(., aes(x = TopRole, y = TL)) +
  geom_boxplot(aes(color = factor(TopRole), fill = factor(TopRole)), alpha=0.9) +
  geom_jitter(size=0.3, aes(color = factor(TopRole), fill = factor(TopRole))) +
  scale_fill_manual(values=cols) +
  labs(x = "Topological role", y = "Trophic level") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title = element_text(size = 10, face = "bold"),
        legend.position = "none")

# Move to a new page
grid.newpage()
# Arrange figure
figure_ab <- ggarrange(plot_sp_bt + rremove("xlab"), plot_sp_cl + rremove("xlab"),
                      labels = c("A","B"), ncol=2,
                      font.label = list(size = 10, color = "black"))
figure_ab <- annotate_figure(figure_ab, bottom = textGrob("Trophic level", gp = gpar(fontface="bold", col="black", fontsize=10)))
figure_4 <- ggarrange(figure_ab,                                                                                         # First row
          ggarrange(plot_sp_ts, plot_sp_tr, ncol = 2, labels = c("C", "D"), font.label=list(color="black",size=10)),                                            
          nrow = 2)
figure_4

@@

# Discussion

## The MPA Namuncurá - Banco Burdwood food web

* The MPA Namuncurá - Banco Burdwood food web is one of the most highly-resolved networks of trophic interactions described for subpolar and polar regions.
Compare network-level properties with other subpolar and polar food webs.

* The food web shows an asymmetry in the distribution of interactions at several levels: food web, functional group, prey and predators. In all of them interactions are concentrated in a few species.
On one hand, this asymmetry indicates that most consumers have a narrow diet, and few present flexible diets (*Patagonotothen guntheri*, *P. ramsayi*, *Dissostichus eleginoides*, *Bathyraja brachyurops*, *B. griseocauda*).
On the other hand few prey are consumed by many predators, meaning that there are dominant food sources from which most consumers depend on: detritus, diatoms (benthic, centric, pennate), and species of *Euphausia*.

## Species' role

@@

* Betweenness. Species at mid-trophic levels (3-4) lie in more shortest paths between species than any other species: ‘bridge’ role. Implications for spread of perturbations like mercury [@Fioramonti2022], microplastics [@Cossi2021].

* Closeness. Low-trophic level species are relatively closer to other species in the food web. Apart from the most demanded food sources (i.e. detritus), which are logically closer to many species, unexpected consumers arise as important in this regard. Species of the zooplankton community like *Calanus* and *Euphausia* are crucial for the food web functioning, since they can affect others more quickly.

* Trophic similarity. Species are more similar at low and mid-trophic levels (2-4). There is a functional redundancy at these levels of the food web. On the other hand, less trophic similarity at high TLs indicate uniqueness in terms of trophic role. This highlights the importance of top predators in the sense that they play a role that cannot be played by any other species.
